Novel Methods for Characterizing Peaks from Direct Injection FT-MS Experiments

### 2019-12-12 peakcharacterization_manuscript.Rmd
better description of the m/z to frequency models that are calculated

Frequency models are calculated for each scan, and the square root term from all scan level models are checked for outliers based on the interquartile ranges across all scans in a sample.
When scan specific models are used for conversion of M/Z to frequency, the peak order observed in M/Z space is not maintained, as shown in Figure XA. 
Therefore, a single model for all scans based on the median of each term in the model across scans is used for converting *all* remaining scan level data.

>>>>

M/Z to frequency models are calculated for each scan, and the square root term from all scan level models are checked for outliers based on the interquartile ranges across all scans in a sample.
While scan specific models **could** be used in the conversion of M/Z to frequency, doing so results in changes to the relative peak ordering compared to M/Z space, as shown in Figure XA. 
Therefore, a single model for all scans based on the median of each term in the model across scans is used for converting *all* remaining scan level data.
